### 2008-03-20 trunk/Papers/dl-gre-08/gre.tex
improved pictures

Consider the following example.  We have three individuals related as indicated in
Figure~\ref{fig-car1}.
\begin{figure}
\begin{center}
\includegraphics[scale=.8]{pic.pdf}
\end{center}
\caption{Distinguishable/indistinguishable points.}\label{fig-car1}
\end{figure}
%
The individuals $i$ and $i'$ can easily be distinguished in first-order logic:
the formula $R(x,x)$ is true of $i$ and false in $i'$. The corresponding
referring expression for $i$ would be ``an individual relating to itself''.
But if we can only use propositional and relational information (equivalently, our grammar does not contain the word ``itself'') then $i$ and $i'$ are indistinguishable. Both
are ``individuals which are related to individuals which are related to individuals\ldots''

@@

\begin{figure}
  \centering
  \includegraphics[width=5cm]{pic-dale-haddock}
  \caption{The Dale and Haddock scenario.}
  \label{fig:dale-haddock}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{pic-el-vs-alc}
  \caption{Illustrating the difference between \el\ and \alc.}
  \label{fig:el-vs-alc}
\end{figure}

>>>>

Consider the following example.  We have three individuals related as indicated in
Figure~\ref{fig:dale-haddock}d.

%\begin{figure}
%\begin{center}
%\includegraphics[scale=.8]{pic.pdf}
%\end{center}
%\caption{Distinguishable/indistinguishable points.}\label{fig-car1}
%\end{figure}
%
The individuals $i$ and $i'$ can easily be distinguished in first-order logic:
the formula $R(x,x)$ is true of $i$ and false in $i'$. The corresponding
referring expression for $i$ would be ``an individual relating to itself''.
But if we can only use propositional and relational information (equivalently, our grammar does not contain the word ``itself'') then $i$ and $i'$ are indistinguishable. Both
are ``individuals which are related to individuals which are related to individuals\ldots''

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{pic-dale-haddock}
  \caption{(a) The \newcite{dale91:_gener_refer_expres_invol_relat}
    scenario; (b) the \newcite{Stone1998a} scenario; (c) illustrating
    the difference between \el\ and \alc; (d)
    distinguishable/indistinguishable points.}
  \label{fig:dale-haddock}
\end{figure*}

% \begin{figure}
%   \centering
%   \includegraphics[width=\columnwidth]{pic-el-vs-alc}
%   \caption{Illustrating the difference between \el\ and \alc.}
%   \label{fig:el-vs-alc}
% \end{figure}
